draft_yma

### 2021-12-14 draft_yma.Rmd
backward forward

```{r}
fit_back = step(full_fit, direction='backward')
fit_back
```

crm_1000 ~ pop + pop18 + hsgrad + bagrad + poverty + 
    pcincome + region + pbeds_1000 + density_pop, data = cdi_model

@@

```{r}
fit_forward = step(full_fit, direction='forward')
fit_forward
```

crm_1000 ~ pop + pop18 + pop65 + hsgrad + bagrad + 
    poverty + unemp + pcincome + region + pdocs_1000 + pbeds_1000 + 
    density_pop, data = cdi_model

@@

```{r}
fit_both = step(full_fit, direction='both')
fit_both
```

>>>>

```{r}
fit_back = step(trans_fit, direction='backward')
fit_back
```

@@

```{r}
fit_forward = step(trans_fit, direction='forward')
fit_forward
```

@@

```{r}
fit_both = step(trans_fit, direction='both')
fit_both
```
